Performing graph-based clustering with rOpenScPCA

### 2024-12-06 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
Add missing chunk name, and regenerate with script

---
title: "Performing graph-based clustering with rOpenScPCA"
date: "`r Sys.Date()`"
author: "Data Lab"
params:
  seed: 2024
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    df_print: paged
---

@@

```{r set seed}
set.seed(params$seed)
```

@@

```{r}
# First, we'll rename the PCA matrix for demonstration
reducedDimNames(sce) <- c("PCA_matrix", "UMAP")
reducedDimNames(sce)

>>>>

---
title: "Performing graph-based clustering with rOpenScPCA"
date: "`r Sys.Date()`"
author: "Data Lab"
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    df_print: paged
---

@@

```{r set seed}
set.seed(2024)
```

@@

```{r use pc_name}
# First, we'll rename the PCA matrix for demonstration
reducedDimNames(sce) <- c("PCA_matrix", "UMAP")
reducedDimNames(sce)
